### 2021-08-14 doc/thesis/chapters/results.tex
re-structure and beautify plot

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}

The hardware utilization of the HLS and VHDL implementations are compared in detail in this section.
The numbers are taken from the final utilization report, that is created by Vivado at the end of the bitstream creation, since this is assumed to be the most accurate report that shows the actual utilization.\\

Figure \ref{fig:hardware_utilization} shows the utilization numbers of different FPGA resources.

\includepicture [0.75] [0, trim=10 10 10 10, clip] {hardware utilization} {hardware_utilization} {img/matlab/hardware_utilization}
